### 2017-01-28 introduction.tex
Minor fixes
intro fixup

Automated test generators tend to produce many failures, which correspond to far fewer faults.  The distribution of faults in a set of failures tends to follow a strong power-law curve, where a few faults account for most failures, and many or even most faults have only 1 or 2 associated failures (even in a set of 1,000 or more test cases) \cite{PLDI13}.  Looking at all the failures to find  distinct faults is impractical.  It is also impractical to apply the iterative approach:  first, fix one test's fault; then re-run all tests, until all tests pass.  There may be some (possibly known) faults that are very difficult to fix. As of 11/20/2015, clang had 89 unresolved, assigned bugs, some dating to 2008.  Knowing if a randomly generated test case is an instance of a known failure can be difficult, and fixing these problems is unlikely.    A research group with a novel fault-detection technique \cite{csmith,ISSTA12,ZhendongPLDI} may dump dozens of new faults on a project at once, and high priority faults may be hidden by stubborn low-priority faults.

@@

Fuzzer taming results using FPF were promising, but limited.  Rather than proposing a universal metric for use in fuzzer taming, Chen et al. offered many possible metrics (based on ideas in the literature, such as edit distances \cite{lev} or coverage spectra \cite{RepsSpectra} methods), none of which performed notably well across all three benchmark data sets, and some of which were not even applicable to all data sets.  For the two most difficult benchmarks, none of the metrics performed extremely well. FPF-based approaches remain in need of a universal but effective metric, particularly for the critical first 50 test cases examined \cite{PLDI13}.

>>>>

Automated test generators tend to produce many failures, which correspond to far fewer faults.  The distribution of faults in a set of failures tends to follow a strong power-law curve, where a few faults account for most failures, and many or even most faults have only 1 or 2 associated failures (even in a set of 1,000 or more test cases) \cite{PLDI13}.  Looking at all the failures to find  distinct faults is impractical.  It is also impractical to apply the iterative approach:  first, fix one test's fault; then re-run all tests, until all tests pass.  There may be some (possibly known) faults that are very difficult to fix. As of 1/16/2017, clang had 109 unresolved, assigned bugs, some dating to 2008 \cite{clangbugs}.  Knowing if a randomly generated test case is an instance of a known failure can be difficult, and fixing long-standing problems to improve bug triage is unlikely.    A research group with a novel fault-detection technique \cite{csmith,ISSTA12,ZhendongPLDI} may dump dozens of new faults on a project at once, and high priority faults may be hidden by stubborn low-priority faults.

@@

Fuzzer taming results using FPF were promising, but limited.  Rather than proposing a universal metric for use in fuzzer taming, Chen et al. offered many possible metrics (based on ideas in the literature, such as edit distances \cite{lev} or coverage spectra \cite{RepsSpectra} methods), none of which performed notably well across all three of their benchmark data sets, and some of which were not even applicable to all data sets.  For the two most difficult benchmarks, none of the metrics performed extremely well. FPF-based approaches remain in need of a universal but effective metric, particularly for the critical first 50 test cases examined \cite{PLDI13}.
